---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# metathis

<!-- badges: start -->
<!-- badges: end -->

[rmarkdown]: https://rmarkdown.rstudio.com
[blogdown]: https://bookdown.org/yihui/blogdown
[Shiny]: https://shiny.rstudio.com
[r4ds]: https://r4ds.had.co.nz/

metathis makes it easy to add HTML `<meta>` tags to your [R Markdown][rmarkdown] or [blogdown] pages and [Shiny] apps.

## Installation

You can install the released version of metathis from [Github](https://github.com/gadenbuie/metathis) with:

``` r
devtools::install_github("gadenbuie/metathis")
```

## Example

This is a basic example that re-creates the metadata tags for the [R for Data Science][r4ds] book. 

```{r example}
library(metathis)

meta() %>%
  meta_description(
    "This book will teach you how to do data science with R..."
  ) %>% 
  meta_name("github-repo" = "hadley/r4ds") %>% 
  meta_viewport() %>% 
  meta_social(
    title = "R for Data Science",
    url = "https://r4ds.had.co.nz",
    image = "https://r4ds.had.co.nz/cover.png",
    image_alt = "The cover of the R4DS book",
    og_type = "book",
    og_author = c("Garrett Grolemund", "Hadley Wickham"),
    twitter_card_type = "summary",
    twitter_creator = "@hadley"
  ) %>% 
  print()
```

## Thanks

Thanks to [Josh Buchea](https://github.com/joshbuchea) for providing an excellent and indispensible resource on `<meta>` tags and other things that go in the HTML `<head>` tags.

And thanks also to [Malcolm Barret](https://github.com/malcolmbarrett). 
Watching over his shoulder as he developed [ymlthis](https://r-lib.github.io/ymlthis) made putting this package together so much easier.

Finally, thanks to the [RStudio team](https://github.com/rstudio) and others who developed [htmltools](https://github.com/rstudio/htmltools) for making HTML in R a breeze.
